
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Education %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace*{-4pt}
\cvsection{Education}

%%%%%%%%%%%%%
%Education 1
%%%%%%%%%%%%%

\cvevent{M.Sc. in Computer Science}{University of St. Gallen (HSG)}{September 2021 -- present}{St. Gallen, Switzerland}

\begin{itemize}
  \item Specialization in Software and System Engineering 
  \item Project and Master Thesis: Framework for local-first applications using conflict-free replicated data types, personal data stores, and Linked Data. 
\end{itemize}

\medskip
%%%%%%%%%%%%%
%Education 2
%%%%%%%%%%%%%

\cvevent{B.Sc. in Computer Science}{Zurich University of Applied Sciences (ZHAW)}{September 2018 -- July 2021}{Winterthur, Switzerland}

\begin{itemize}
  \item Bachelor thesis: \textit{Neural Network-based Image Synthesis to Improve Automatic Segmentation of Medical Images for COVID Diagnosis}
  \item Electives in information engineering, optimization, analysis, and AI
  \item GPA 5.4/6, completed International Profile (IP).
\end{itemize}

\cvevent{}{Sungkyunkwang University (SKKU)}{August 2020 -- January 2021}{Seoul, South Korea}

\begin{itemize}
  \item Exchange semester with electives in multiple ML and DL courses, computer security, web, and financial management. GPA 4.41/4.5
\end{itemize}

\medskip
%%%%%%%%%%%%%
%Education 3
%%%%%%%%%%%%%

\cvevent{Professional Baccalaureate}{Bildungszentrum für Technik Frauenfeld}{August 2016 -- July 2017}{Frauenfeld, Switzerland}

\begin{itemize}
  \item Award winning engineering report about a temporary wooden bridge
  \item Graduated as best of year, grade 5.7/6
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Experience %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Experience}

%%%%%%%%%%%%%
%Experience 0
%%%%%%%%%%%%%

\cvevent{Teaching Assistant}{University of St. Gallen}{September 2022 -- present}{St. Gallen, Switzerland}

\begin{itemize}
    \setlength{\itemindent}{0.5em}
    \item[--]  \textbf{Grundlagen Business Innovation:} Conducted a practice lecture for 99 master students, covering programming fundamentals and basic architecture principles.
    \item[--]  \textbf{Programming Methodologies:} Conducted practice lectures for 35 bachelor students covering Java fundamentals and advanced concepts.
\end{itemize}

\medskip

%%%%%%%%%%%%%
%Experience 1
%%%%%%%%%%%%%

\cvevent{Data Science Internship}{Factory Data S.A.}{July 2021 -- September 2021}{Lleida, Spain}

\begin{itemize}
    \setlength{\itemindent}{0.5em}
    \item[--]  I contributed to the development and deployment of data processing and statistical pipelines using PySpark. 
    \item[--]  I proposed and implemented continuous integration (CI) with automated testing using Docker and GitHub Actions, improving the efficiency and reliability of the data processing. 
\end{itemize}

\medskip

%%%%%%%%%%%%%
%Experience 2
%%%%%%%%%%%%%
\newpage

\cvevent{Assembly Carpenter}{Gebr. Bissegger Schreinerei GmbH}{November 2017 -- September 2018}{Altnau, Switzerland}

\begin{itemize}
    \setlength{\itemindent}{0.5em}
    \item[--] Led projects and supervised teams, interacting with clients to ensure their needs were met.
\end{itemize}

\medskip


%%%%%%%%%%%%%
%Experience 3
%%%%%%%%%%%%%

\cvevent{Cabinet Maker}{Marquart Innenausbau AG}{November 2015 -- April 2016}{Romanshorn, Switzerland}

\begin{itemize}
    \setlength{\itemindent}{0.5em}
    \item[--] Produced and assembled store interiors for national chains.
\end{itemize}

\medskip

%%%%%%%%%%%%%
%Experience 4
%%%%%%%%%%%%%

\cvevent{Apprenticeship Carpentry}{H \& L Rüegge Schreinerei}{August 2011 -- October 2015}{Romanshorn, Switzerland}


\begin{itemize}
    \setlength{\itemindent}{0.5em}
    \item[--] Completed a Schreiner (Carpenter) EFZ apprenticeship with a grade of 5.4/6.
\end{itemize}

\medskip